Removal only

### 2020-05-29 analysis/figure-4.Rmd
better suppl files

  p <- df %>%
    dplyr::filter(gene  == whichgene, 
                  treatment %in% timinglevels,
                  !treatment %in%  c("control", "bldg", "inc.d3"))  %>%
    ggplot(aes(y =  counts, x = treatment, fill = treatment, color = sex)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    theme_B3() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          plot.subtitle = element_text(face = "italic")) +
    scale_color_manual(values = allcolors) +
    scale_fill_manual(values = allcolors)  +
    labs(title = paste(whichtissue, sep = " "), subtitle = whichgene, y = "gene expression") +
    geom_signif(comparisons = list(c("inc.d9", "early"), 
                                  c( "inc.d17", "prolong"), c( "prolong", "hatch"),
                                  c( "hatch", "extend"), c( "n5", "extend")),
                map_signif_level=TRUE,
                textsize = 3, family = 'Helvetica',
                vjust = 1.5, size = 0.5) 
  return(p)

>>>>

  p <- df %>%
    dplyr::filter(gene  == whichgene, 
                  treatment %in% timinglevels,
                  !treatment %in%  c("control", "bldg", "inc.d3"))  %>%
    ggplot(aes(y =  counts, x = treatment, fill = treatment, color = sex)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    theme_B3() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          plot.subtitle = element_text(face = "italic")) +
    scale_color_manual(values = allcolors) +
    scale_fill_manual(values = allcolors)  +
    labs(title = paste(whichtissue, sep = " "), subtitle = whichgene, y = "gene expression") +
    geom_signif(comparisons = list(c("inc.d9", "early"), 
                                  c( "inc.d17", "prolong"), c( "prolong", "hatch"),
                                  c( "hatch", "extend"), c( "n5", "extend")),
                map_signif_level=TRUE,
                textsize = 1.5, family = 'Helvetica',
                vjust = 1.5, size = 0.5) 
  return(p)
